---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


### Loading and peaking into the data

```{r}

unzip(zipfile = "activity.zip")
raw_data <- read.csv("activity.csv")

```

### Processing: removing NA from data

```{r}

good <- complete.cases(raw_data)
data <- raw_data[good,] 

head(data)

```


### Calculate the total number of steps taken per day

```{r}

steps_per_day <- aggregate(data$steps, by=list(day = data$date), "sum")
head(steps_per_day)

```


### Make a histogram of the total number of steps taken each day

```{r}

hist(steps_per_day$x, main="Histogram", xlab="Steps per day")
 
```

### Calculate and report the mean and median of the total number of steps taken per day

#### Mean 

```{r}
mean(steps_per_day$x)
```

#### Median 

```{r}
median(steps_per_day$x)
```


### What is the average daily activity pattern?

 
Make a time series plot (i.e. ðšðš¢ðš™ðšŽ = "ðš•") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)

```{r}

require(graphics)

activity <- aggregate( formula = steps~interval, 
           data = data,
           FUN = mean)

#peak into the data
head(activity)

#show plot
plot(activity , type="l") 

```

### Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?

```{r}
#get the active interval
active_interval <- activity[which.max(activity$steps),]

#print the interval
active_interval

#get the hour
hr <- active_interval / 60

#this could need converting into hh:mm, but I guess for purpose of homework, this is enough
hr

```

### Imputing missing values

Calculate and report the total number of missing values in the dataset (i.e. the total number of rows with ð™½ð™°s)

```{r}

total_na <- sum(is.na(raw_data$steps))

total_na

```

###  Fill the missing values data

```{r}

fill.value <- function(steps, interval) {
    filled <- NA
    if (!is.na(steps)) 
        filled <- c(steps) else filled <-  activity$steps[ which(activity$interval == interval )]
    return(filled)
}

new_data <- raw_data

new_data$steps <- mapply(fill.value, new_data$steps, new_data$interval)

new_activity <- aggregate( formula = new_data$steps~new_data$interval, 
           data = new_data,
           FUN = mean)

plot(activity, type="l")

plot(new_activity, type="l")
```

### Are there differences in activity patterns between weekdays and weekends?

```{r}
add_week_flag <- function(date) {
    day <- weekdays(date)
    if (day %in% c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday")) 
        return("midweek") else if (day %in% c("Saturday", "Sunday")) 
        return("weekend") else stop("invalid date")
}

new_data$date <- as.Date(new_data$date)

new_data$day <- sapply(new_data$date, FUN = add_week_flag)

## I haven't completed the full R course yet, there has to be a better way to do this.
midweek_data <- subset(new_data, day=="midweek")

weekend_data <- subset(new_data, day=="weekend")


##head(weekend_data , 5000L)
 
activity_midweek <- aggregate( formula = steps~interval, 
           data= midweek_data,
           FUN = mean)

plot(activity_midweek , type = "l")

activity_weekend <- aggregate( formula = steps~interval, 
           data= weekend_data,
           FUN = mean)

plot(activity_weekend, type = "l" )

``` 
