---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


### Loading and peaking into the data

```{r}

unzip(zipfile = "activity.zip")
data <- read.csv("activity.csv")


```

### Processing: removing NA from data

```{r}

good <- complete.cases(data)
data <- data[good,] 

head(data)

```


### Calculate the total number of steps taken per day

```{r}

steps_per_day <- aggregate(data$steps, by=list(day = data$date), "sum")
head(steps_per_day)


```


### Make a histogram of the total number of steps taken each day

```{r}

hist(steps_per_day$x, main="Histogram", xlab="Steps per day")
 
```

### Calculate and report the mean and median of the total number of steps taken per day

```{r}
mean(steps_per_day$x)
median(steps_per_day$x)
```


## What is the average daily activity pattern?

 
Make a time series plot (i.e. ðšðš¢ðš™ðšŽ = "ðš•") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)

```{r}

require(graphics)

activity <- aggregate( formula = steps~interval, 
           data = data,
           FUN = mean)



head(activity)
 
  
plot(activity , type="l") 

active_interval <- activity[which.max(activity$steps),]

active_interval

hr <- active_interval / 60

hr

```

### Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?


## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
