---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


### Loading and peaking into the data

```{r}

unzip(zipfile = "activity.zip")
raw_data <- read.csv("activity.csv")


```

### Processing: removing NA from data

```{r}

good <- complete.cases(raw_data)
data <- raw_data[good,] 

head(data)

```


### Calculate the total number of steps taken per day

```{r}

steps_per_day <- aggregate(data$steps, by=list(day = data$date), "sum")
head(steps_per_day)


```


### Make a histogram of the total number of steps taken each day

```{r}

hist(steps_per_day$x, main="Histogram", xlab="Steps per day")
 
```

### Calculate and report the mean and median of the total number of steps taken per day

```{r}
mean(steps_per_day$x)
median(steps_per_day$x)
```


## What is the average daily activity pattern?

 
Make a time series plot (i.e. ðšðš¢ðš™ðšŽ = "ðš•") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)

```{r}

require(graphics)

activity <- aggregate( formula = steps~interval, 
           data = data,
           FUN = mean)

head(activity)

plot(activity , type="l") 

```

### Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?

```{r}
active_interval <- activity[which.max(activity$steps),]

active_interval

hr <- active_interval / 60

hr
```

## Imputing missing values

Calculate and report the total number of missing values in the dataset (i.e. the total number of rows with ð™½ð™°s)

```{r}

total_na <- sum(is.na(raw_data$steps))

total_na

```

filling data for the mean for that 5-minute interval, etc.

```{r}

fill.value <- function(steps, interval) {
    filled <- NA
    if (!is.na(steps)) 
        filled <- c(steps) else filled <-  activity$steps[ which(activity$interval == interval )]
    return(filled)
}

new_data <- raw_data

head(new_data)

new_data$steps <- mapply(fill.value, new_data$steps, new_data$interval)

head(new_data)

par(mfrow = c(2, 1))   

new_activity <- aggregate( formula = new_data$steps~new_data$interval, 
           data = new_data,
           FUN = mean)

plot(activity, type="l")
plot(new_activity, type="l")

``` 
## Are there differences in activity patterns between weekdays and weekends?
